\documentclass{article}

\begin{document}

  \section{Isaac Benjamin Goss}
    ibg4@pitt.edu
    (412) 478-3219
    %Address
    307 S. Maple Street, Greensburg, PA 15601
    
  \section{Education}
    \subsection{University of Pittsburgh}
      %Right align this
      (August 2014 - May 2018)
      \begin{itemize}
        \item Bachelor of Science in Computer Engineering
        \item Minor in Mathematics
      \end{itemize}
      GPA: 3.5/4.0 | Dean's List
  
  \section{Experience}
    \subsection{North American Malignant Hyperthermia Registry}
      (November 2015 - Present)
      Work Study Student
      \begin{itemize}
        \item Assist in designing data collection forms.
        \item Assist our push to move data into a new system.
        \item Perform basic data cleansing.
        \item Perform various tasks which ensure our data is up-to-date.
      \end{itemize}
    \subsection{University of Pittsburgh}
      (January 2015 - May 2015)
      Mathematics Tutor
      \begin{itemize}
        \item Supplement in-classroom learning with personal attention in Calculus classes 1, 2, and 3, and Physics 1.
        \item Ask the right questions so that a student can find the answer by herself.
        \item Answer questions that would help a student understand.
      \end{itemize}
    \subsection{Shoener Environmental}
      (June 2014 - November 2014)
      Environmental Technician
      \begin{itemize}
        \item Collect data about the effects of wind turbines on local bird and bat populations.
        \item Extract and categorize fallen animals.
        \item Maintain the search area, keeping it easy to navigate.
      \end{itemize}
    \subsection{Radio Shack}
      (December 2013 - July 2014)
      Sales Associate
      \begin{itemize}
        \item Solve customer problems by offering a complete solution.
        \item Provide general technical assistance to my customers.
        \item Work on the customer's behalf, including activating cell phone contracts, and processing repairs and returns.
      \end{itemize}
    \subsection{Pennsylvania Highlands Community College}
      (September 2013 - May 2014)
      Mathematics Tutor
      \begin{itemize}
        \item Solidify classroom concepts so that my students could understand mathematics. 
        \item Helped students better understand material ranging from Basic Math to Calculus 1, and General Chemistry 1.
        \item Schedule appointments to meet with an average of seven students a week.
      \end{itemize}
    
  \section{Skills}
    \subsection{Communication}
      \begin{itemize}
        \item Comfortable Presenting Publicly (Musical performance, Speech class)
        \item 
        \item 
      \end{itemize}
    \subsection{Software Development}
      \begin{itemize}
        \item Java(Swing),Python(NumPy,SciPy,pandas?),MIPS,RegEx,SQL, LaTeX?
        \item Git
        \item to learn: Data Structures
      \end{itemize}
    \subsection{Electronics}
      \begin{itemize}
        \item A&D with standard linear devices, diodes, transistors
        \item Use of Boolean algebra and finite state machine abstraction to describe logical circuits.
        \item Designed my own microprocessor to implement MIPS
      \end{itemize}
    \subsection{Mathematics}
      \begin{itemize}
        \item Calculus, DiffEq, Linear Algebra, Proofs, Boolean Algebra
        \item Tutor Basic Math to Calc 3
        \item RSA cipher
      \end{itemize}
    \subsection{Problem Solving}
      \begin{itemize}
        \item 
        \item 
        \item 
      \end{itemize}
    \subsection{Critical Thinking}
      \begin{itemize}
        \item 
        \item 
        \item 
      \end{itemize}
    \subsection{Collaboration}
      \begin{itemize}
        \item 
        \item 
        \item 
      \end{itemize}
    \subsection{Leadership}
      \begin{itemize}
        \item 
        \item 
        \item 
      \end{itemize}
    
\end{document}